Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-08-23 writeup/conStruct.tex
getting tex to compile

\newpage
\section*{Introduction}
A fundemental quandary in the description of biological diversity, is
the fact that diversity shows both discrete and continuous patterns. 
For example, there is disagreement on species concepts because the
process of speciation is usually gradual, and so there is no set point
in the continuous divergence of populations when they become discrete species.
This issue extends below the species level as patterns of phenotypic
and genetic diversity within and among populations are shaped
by continuous migration and drift, as well as more discrete events and
processes such as geographic barriers, rapid expansions, bottlenecks, and rare
long distance migration.

>>>>

\newpage
\section*{Introduction}
A fundamental quandary in the description of biological diversity is
the fact that diversity shows both discrete and continuous patterns. 
For example, there is disagreement on species concepts because the
process of speciation is usually gradual, and so there is no set point
in the continuous divergence of populations when they unambiguously become discrete species.
This issue extends below the species level, as patterns of phenotypic
and genetic diversity within and among populations are shaped
by continuous migration and drift, as well as by more discrete events, 
such as geographic barriers, rapid expansions, bottlenecks, and rare
long distance migration.
